TO FIND

### 2013-05-23 ms.tex
First paragraphs of the discussion

The model is neutral because it assumes that the probabilities of a local
recruitment, an immigration and a mortality event are all equal across species. Demographic
stochasticity is the source of variations in abundance, but larger disturbances
could be simulated as well, as long as they hit all species with the same
probability, independently of their density. The fundamental feature of neutral
dynamics is therefore the ecological drift, defined as population changes
emerging from neutraly stable population dynamics. It can be measured as the
variance between replicated time series of community dynamics
\parencite{Gravel2011}. \textcite{Hubbell2001} provides a very comprehensive
analysis of the model, with specific attention to the effect of the different
parameters on the drift (and consequently variance in abundance) and time to
extinction. Despite its simplicity, the neutral model is surprisingly rich in
the predictions it makes. \textcite{Bell2001} and \textcite{Hubbell2001}
analyzed the performance of neutral models to predict species abundance
distributions, range-abundance relationship, spatial variation in abundance,
species-area relationship, community turnover (beta-diversity) and
co-occurrence. Recent trophic neutral models also predicted realistic ecological networks \parenciteCanard2012}. Other than the ecological equivalence assumption, one of the most
criticized aspect of neutral models is the realism of the speciation process and
the required speciation rates to sustain species richness
\parencite{Ricklefs2003,Etienne2007}. Recent neutral models with more credible
speciation models \parencite{Rosindell2009,Desjardins2012a} revealed the
difficulty to maintain diversity in neutral models over macro-evolutionary time
scales. These models however also generated interesting novel predictions on
endemic species richness \parencite{Rosindell2011,Desjardins2012b}.

@@

In Fig. 2, we present the species richness of each node of the network (alpha diversity), as a function of
the centrality of the node, under different assumptions of metacommunity
dynamics and network structure. We scaled the species richness by the maximal local species richness to 
facilitate comparison between models. The model parameterization is responsible for differences in both alpha and gamma diversity.  It appears that both in the goeographical and
tree graph, the path dynamics model has a much more considerable variation in local species richness. 
However, in all cases the alpha diversity increases with the node centrality, whether it is
measured by the degree or the eigencentrality. All situations examined give a
remarkably congruent signal.

% TO CHANGE WITH NEW FIGURE (SCALED DIVERSITY)
%The patch dynamics model, \emph{i.e.} when there
%are no interactions between species, allows more $\alpha$ diversity. The neutral
%model allowed the maintenance of slightly more diversity than the
%species-sorting model. In all cases however, it is clear that the richness
%maintained tend to increase with the node centrality.

@@

To a vast extent, these relationships are preseved when looking at the
topological distances (Fiig. 4), i.e. along how many edges should one travel to connect
two patchs. Interestingly enough, the distance-dissimilarity relationship for
the neutral model is markedly hump-shaped, with sites being at a medium distance
having the maximal dissimilarity.

@@

%TP:
Contrasting the three perspectives: what do we learn?

%TP OR DG
Network approach brings spatial variation in coexistence mechanisms; emergent properties
	- role of the degree distribution
%DG
Making the theory operational
	- how to parameterize neutral models
	- making predictions for specific landscapes

>>>>

The model is neutral because it assumes that the probabilities of a local
recruitment, an immigration and a mortality event are all equal across species. Demographic
stochasticity is the source of variations in abundance, but larger disturbances
could be simulated as well, as long as they hit all species with the same
probability, independently of their density. The fundamental feature of neutral
dynamics is therefore the ecological drift, defined as population changes
emerging from neutraly stable population dynamics. It can be measured as the
variance between replicated time series of community dynamics
\parencite{Gravel2011}. \textcite{Hubbell2001} provides a very comprehensive
analysis of the model, with specific attention to the effect of the different
parameters on the drift (and consequently variance in abundance) and time to
extinction. Despite its simplicity, the neutral model is surprisingly rich in
the predictions it makes. \textcite{Bell2001} and \textcite{Hubbell2001}
analyzed the performance of neutral models to predict species abundance
distributions, range-abundance relationship, spatial variation in abundance,
species-area relationship, community turnover (beta-diversity) and
co-occurrence. Recent trophic neutral models also predicted realistic ecological networks \parencite{Canard2012}. Other than the ecological equivalence assumption, one of the most
criticized aspect of neutral models is the realism of the speciation process and
the required speciation rates to sustain species richness
\parencite{Ricklefs2003,Etienne2007}. Recent neutral models with more credible
speciation models \parencite{Rosindell2009,Desjardins2012a} revealed the
difficulty to maintain diversity in neutral models over macro-evolutionary time
scales. These models however also generated interesting novel predictions on
endemic species richness \parencite{Rosindell2011,Desjardins2012b}.

@@

In Fig. 2, we present the species richness of each node of the network (alpha
diversity), as a function of the centrality of the node, under different
assumptions of metacommunity dynamics and network structure. We scaled the
species richness by the maximal local species richness to facilitate comparison
between models. The model parameterization is responsible for differences in
both alpha and gamma diversity and thus prevents meaningful absolute
comparisons. It appears that both in the geographical and random tree graphs,
the path dynamics model has a much more considerable variation in local species
richness. However, in all cases the alpha diversity increases with the node
degree centrality and not so much with eigencentrality. There are some clear
differences among metacommunity perspectives. First, the relationship between
degree centrality and species richness is strongest for patch dynamics, followed
by neutral dynamics and then species sorting. Second, there is apparently much
more scatter in the species sorting scenario. Thirdly, the richness-centrality
relationship appears weaker for the random tree graph.

@@

To a vast extent, these relationships are preseved when looking at the
topological distances (Fig. 4), i.e. along how many edges should one travel to
connect two patchs. Interestingly enough, the distance-dissimilarity
relationship for the neutral model is markedly hump-shaped, with sites being at
a medium distance having the maximal dissimilarity.

@@

Our objective in this paper was to review the main assumptions of three
metacommunity models and illustrate how the implementation of more realistic
landsapes could reveal the importance of dispersal on community structure. We
argued in the introduction that neutral theory is useful both to understand and
predict the impact of dispersal on community organization. The review of the
different models shows that the fundamental difference between a neutral model
and the patch dynamics model is the effect of competitive interactions on
distribution, while the difference between the neutral and the species sorting
models is the effect of unequal competitive interactions. The neutral model is
thus a usefull tool to understand the joint effects of dispersal and community
interactions. Our comparison of the distribution of alpha diversity was
particularly meaningful in that respect. The simulation results show that
competitive interactions buffer the potential impact of landscape structure. The
strongest centrality-species richness relationship was observerd for the patch
dynamics, a model without any interactions. On the other hand, strong and
unequal competitive interactions minimized the effect of centrality. Our model
analysis greatly illustrates the growing recognition in metacommunity ecology
that we must move toward more realistic landscapes \parencite{Gilarranz2012}.
For field ecologists, and particularly limnologists, our review emphasize that
we need to go beyond geographic based analysis of beta-diversity (e.g.
\parencite{Legendre2005}) to topological based analyses \parencite{Peterson2013}.

The network approach to the study of spatially explicit landscapes is a major
advancement in metacommunity ecology. It is a first step to make the concept
operational because it accounts for more realistic landscape structures and
dispersal kernels. It makes a significant departure to simple island-mainland or
global dispersal approaches used previously (e.g. \parencite{Tilman1994,
Mouquet2002, Hubbell2001}). But dispersal is also spatially explicit in a
lattice model and it does not make the landscape more realistic. We believe the
fundamental contribution of this approach is the consideration of spatial
heterogeneity of dispersal. In agreement with previous theoretical
\parencite{Economo2011, Desjardins2012} and experimemental studies
\parencite{Altermat2012}, the simulations show that the degree centrality has a
significant impact on local species richness. Central nodes might also
contribute more to maintain regional diversity, as they are essential for
species to spread throughout the landscape. The nodes could be potentially
quantified as keystone for the metacommunity \parencite{Mouquet2013}.
Interestingly, but not surprisingly, this effect is weaker with species sorting
dynamics. We could even hypothesize it will vanish in the extreme case of niche
differentiation (with low overlap for instance) and low mass effect. The neutral
versus niche comparison therefore illustrates that very strong unequal
competitive interactions could overwhelm the impact of dispersal.

The network approach and the comparison between metacommunity perspectives
reveal there could be spatial variation in coexistence mechanisms. If we take
the species-sorting perspective for instance, we find that alpha diversity is
higher in more central nodes. Since the environment is constant, it implies that
diversity in these communities is maintained by a stronger mass effect. It
results in spatial variation in the relative importance of species-sorting, the
mass effect and to a certain extent the neutral drift. Because the degree
centrality was the best variable explaining diversity, we should expect the
degree distribution to strongly impact the relative importance of these
coexistence mechanisms. For a given set of ecological processes and distribution
of species traits, we might expect the coexistence mechanisms to differ from one
landscape to another.

We introduced this article arguing that neutral theory could be used as an
instrument to predict species distribution in spatially heterogeneous
landscapes. So far we have treated only theoretical models, but we could also
envision to parameterize them and simulate real landscapes. The recruitment
probabilities defined above could be used as satistical models (likelihood
functions) to fit to empirical data. Prior information could be used to define
apriori dispersal kernels and then fit the model as in \textcite{Gravel2008}.
The fit of metapopulation models to spatially explicit landscapes was pionneered
by \textcite{Hanski1998} and recently extended to species distribution models
including both species sorting and dispersal limitations
\parencite{Boulangeat2012}. Given the parameterization, one could run neutral
models to generate null hypotheses that could be eventually compared to observed
distribution. This would make a significant improvement over traditional null
models in ecology (Gotelli1996) where there are no interactions and no dispersal
limitations.

The multivariate variance partitioning framework originally proposed by Borcard
et al. (1992) and further developped by Borcard and Legendre (2002) has been
widely used to quantify the relative importance of species sorting and dispersal
limitations in species distribution. This framework was originally proposed to
model species distribution as a function of environmental variables, taking into
accound the spatial autocorrelation of species distriution (Leduc1992,
Borcard1992, Legendre1993). This methodology has been widely used over the last
decade as a test of the neutral theory, its underlying assumption and a
quantification of dispersal limitations (e.g. Svenning2004; Hardy2004;
Gilbert2004; Cottenie2005). One problem of this approach is however that it
makes a weak test of neutrality (McGill2003), based on the description of
spatial community structure, rather than hypothesis testing. The different
models we reviewed in this article could be better employed if used to generate
expectations based on different hypotheses and then compare them. But most of
all, parameterized spatially explicit neutral models could be more useful if
used to generate expectations. For instance, neutral models could be used to
predict the consequences of habitat destruction, fragmentation or a change in
the connectinity matrix \parencite{Hubbell2008}. The spatially explicit
description of the landscape is a major improvement toward that end, providing
much flexibility in the scenarios that could be explored.
